TODO title

### 2017-01-13 doc/paper/paper.tex
Minor fixes in paper.

To evaluate the two mechanisms we use a number of metrics. First we determine 
whether the model is able to form a clear decision at all within a second of 
simulated time. To count as a clear decision at least one output needs to stay 
above 0.2 for a second after the initial second of simulation time. This ensures 
that the output is different from a 0 output which could slightly be above 
0 due to noise. Furthermore, we require that the largest output will be the 
  largest output for all of that second of simulation time because otherwise the 
  decision would switch.

@@

The time required to reach a decision in the Usher-McClelland model depend 
mostly on the target separation and amount of noise on the input (Figure~TODO), 
the magnitude of the largest input is of minor influence. In contrast to that, 
in the independent accumulator model the scaled magnitude of the largest input 
is the most important factor. Depending on this magnitude the network can either 
be faster or slower than the Usher-McClelland network, but it will need more 
time to achieve the same corectness of responses. There is also a slight 
influence of target separation and input noise with an interaction of these two 
parameters (Figure~TODO).

>>>>

To evaluate the two mechanisms we use a number of metrics. First we determine 
whether the model is able to form a clear decision at all within a second of 
simulated time. To count as a clear decision at least one output needs to stay 
above 0.15 for a second after the initial second of simulation time. This 
ensures that the output is different from a 0 output which could slightly be 
above 
0 due to noise. Furthermore, we require that the largest output will be the 
  largest output for all of that second of simulation time because otherwise the 
  decision would switch.

@@

The time required to reach a decision in the Usher-McClelland model depend 
mostly on the target separation and amount of noise on the input (Figure~TODO), 
the magnitude of the largest input is of minor influence. In contrast to that, 
in the independent accumulator model the scaled magnitude of the largest input 
is the most important factor. Depending on this magnitude the network can either 
be faster or slower than the Usher-McClelland network, but it will need more 
time to achieve the same correctness of responses. There is also a slight 
influence of target separation and input noise with an interaction of these two 
parameters (Figure~TODO).
